Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-14 papers/assembly/I/main.tex
[paper] Highlight a major error in the formalism

@@

\begin{definition}\label{def:basis}
    Let $P$ be a Petri net and let $\B$ be a non-empty subset of sites of $P$.
    We say that $\B$ is a \textbf{basis} of $P$ if $P = \upset{\B}$ such that if $U \subseteq \B$ with $P = \upset{U}$ then $U = \B$.
\end{definition}

>>>>

{
    \color{red}

    {
        \large
        \noindent \textbf{MAJOR PROBLEM:} the following three definitions are flawed in that loops gum up the works.
        The previous example is demonstrative.
        Every site lies within the upper subset of every other site.
        Pick any one and call the singleton set containing it $\B$; it is minimal.
        These two facts combined means that $\B$ is a basis, but \textbf{we don't want that!}.
        Ideally, the possible bases should be $\{A, B, C\}$, $\{AA, AB, C\}$ and $\{C, AAAB\}$.

        I think we see the source of this problem in the example of minimal elements below.
        $C$ should be minimal, but it is not because there are pathways that lead to it, e.g. $\gamma$ from $AA$.
        The solution, in my mind, is to somehow merge the definition of a pathway and the site completion, and slightly modify the definition of a minimal element.
    }

    In some Petri nets, there exist sites to which no pathways lead.
    Consider, for example, the subnet of our ligation network which leaves out the $\delta$ transition:

    \begin{center}
        \color{black}
        \scalebox{0.6}{
            \begin{tikzpicture}
                \begin{pgfonlayer}{nodelayer}
                    \node [style=site, draw=red] (A) at (0, 0.8) {$A$};
                    \node [style=site] (B) at (0, -0.8) {$B$};
                    \node [style=site, draw=red] (C) at (6, -1.6) {$C$};
                    \node [style=site, draw=red] (AA) at (4, 0.8) {$AA$};
                    \node [style=site, draw=red] (AB) at (4, -0.8) {$AB$};
                    \node [style=site, draw=red] (AAAB) at (8, 0) {$AAAB$};
                    \node [style=transition, fill=green!20, draw=red] (tau1) at (2, 0.8) {$\alpha$};
                    \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                    \node [style=transition, fill=green!20, draw=red] (tau3) at (6, 0) {$\gamma$};
                \end{pgfonlayer}
                \begin{pgfonlayer}{edgelayer}
                    \draw [style=arrow, bend right=15] (A) to (tau1);
                    \draw [style=arrow, bend left=15] (A) to (tau1);
                    \draw [style=arrow, bend right=15] (A) to (tau2);
                    \draw [style=arrow] (tau1) to (AA);
                    \draw [style=arrow] (B) to (tau2);
                    \draw [style=arrow] (tau2) to (AB);
                    \draw [style=arrow] (AA) to (tau3);
                    \draw [style=arrow] (AB) to (tau3);
                    \draw [style=arrow, bend left=30] (C) to (tau3);
                    \draw [style=arrow] (tau3) to (AAAB);
                    \draw [style=arrow, bend left=30] (tau3) to (C);
                \end{pgfonlayer}
            \end{tikzpicture}
        }
    \end{center}

@@

    \begin{definition}\label{def:basis}
        Let $P$ be a Petri net and let $\B$ be a non-empty subset of sites of $P$.
        We say that $\B$ is a \textbf{basis} of $P$ if $P = \upset{\B}$ such that if $U \subseteq \B$ with $P = \upset{U}$ then $U = \B$.
    \end{definition}
}
